---
title: "lab5"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab5}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(lab5)
```

# Introduction

This is prgram which can access to data from Kolada. It consists of a class named rkolada.

# Example

You can run this code to initialize a rkolada class.

```{r rkolada example}
object <- rkolada()
```

Besides, there are some functions provided to access data: \## GetAndSetKpiSearchData: This function returns data based on the KPI title and set member variable.

```{r}
object$GetAndSetKpiSearchData(searchStr = "Skatt")
```

## GetAllData

This function returns data based on the KPI ID, municipality and year.

```{r }
object$GetAllData(kpi_id = "N00903", municipality = "1281", year = "2009")
```

## GetKpiData:

This function returns data based on the KPI title, but directly return data.

```{r}
object$GetKpiData(kpiString = "Skatt")
```

## GetManicipalityData

This fucntion returns data based on municipality ID.

```{r}
object$GetManicipalityData(municipalityString = "Lund")
```
